---
title: "Detailed changes"
author: "Julie Sheard"
date: "30/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
This is the script to look at individual species trends within different time periods based on the direction of occupancy change.

## Load packages
```{r}
library(sparta)
library(bayestestR)
```

## Load data, 50,000 iterations
```{r}
load("C:/Users/julie/Documents/Projects/Occupancy/output/para_out_50_nyr.RData")

para_out <- para_out_50

for(i in 1:length(para_out)) names(para_out)[i] <- para_out[[i]]$SPP_NAM

```


#Species with 50,000 iterations
##Camponotus herculeanus, continuous increase
```{r}
cdiff<-para_out$Camponotus_herculeanus$BUGSoutput$sims.matrix[,40]-para_out$Camponotus_herculeanus$BUGSoutput$sims.matrix[,34]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica cinerea, no change
```{r}
cdiff<-para_out$Formica_cinerea$BUGSoutput$sims.matrix[,40]-para_out$Formica_cinerea$BUGSoutput$sims.matrix[,34]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi

```

##Formica cunicularia, no change
```{r}
cdiff<-para_out$Formica_cunicularia$BUGSoutput$sims.matrix[,40]-para_out$Formica_cunicularia$BUGSoutput$sims.matrix[,38]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```
##Formica polyctena, mixed
```{r}
cdiff<-para_out$Formica_polyctena$BUGSoutput$sims.matrix[,40]-para_out$Formica_polyctena$BUGSoutput$sims.matrix[,38]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica pressilabris, no change
```{r}
cdiff<-para_out$Formica_pressilabris$BUGSoutput$sims.matrix[,40]-para_out$Formica_pressilabris$BUGSoutput$sims.matrix[,37]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica rufa, Mixed
```{r}
cdiff<-para_out$Formica_rufa$BUGSoutput$sims.matrix[,36]-para_out$Formica_rufa$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica rufibarbis, Mixed
```{r}
cdiff<-para_out$Formica_rufibarbis$BUGSoutput$sims.matrix[,32]-para_out$Formica_rufibarbis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica sanguinea, mixed
```{r}
cdiff<-para_out$Formica_sanguinea$BUGSoutput$sims.matrix[,33]-para_out$Formica_sanguinea$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica truncorum, no change
```{r}
cdiff<-para_out$Formica_truncorum$BUGSoutput$sims.matrix[,32]-para_out$Formica_truncorum$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica uralensis
```{r}
cdiff<-para_out$Formica_uralensis$BUGSoutput$sims.matrix[,31]-para_out$Formica_uralensis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formicoxenus nitidulus
```{r}
cdiff<-para_out$Formicoxenus_nitidulus$BUGSoutput$sims.matrix[,31]-para_out$Formicoxenus_nitidulus$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Lasius fuliginosus 
```{r}
cdiff<-para_out$Lasius_fuliginosus$BUGSoutput$sims.matrix[,31]-para_out$Lasius_fuliginosus$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Lasius umbratus 
```{r}
cdiff<-para_out$Lasius_umbratus$BUGSoutput$sims.matrix[,36]-para_out$Lasius_umbratus$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica rubra
```{r}
cdiff<-para_out$Myrmica_rubra$BUGSoutput$sims.matrix[,31]-para_out$Myrmica_rubra$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica ruginodis
```{r}
cdiff<-para_out$Myrmica_ruginodis$BUGSoutput$sims.matrix[,31]-para_out$Myrmica_ruginodis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica rugulosa
```{r}
cdiff<-para_out$Myrmica_rugulosa$BUGSoutput$sims.matrix[,30]-para_out$Myrmica_rugulosa$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica sabuleti
```{r}
cdiff<-para_out$Myrmica_sabuleti$BUGSoutput$sims.matrix[,33]-para_out$Myrmica_sabuleti$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
Firsthi
Lasthi
ci_eti
```

##Myrmica scabrinodis
```{r}
cdiff<-para_out$Myrmica_scabrinodis$BUGSoutput$sims.matrix[,33]-para_out$Myrmica_scabrinodis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica schencki
```{r}
cdiff<-para_out$Myrmica_schencki$BUGSoutput$sims.matrix[,30]-para_out$Myrmica_schencki$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

#Load data, 100,000 iterations

```{r}
load("C:/Users/julie/Documents/Projects/Occupancy/output/para_out_100_nyr.Rdata") 

para_out <- para_out_100

for(i in 1:length(para_out)) names(para_out)[i] <- para_out[[i]]$SPP_NAM
```

#Species with 100,000 iterations
##Formica fusca
```{r}
cdiff<-para_out$Formica_fusca$BUGSoutput$sims.matrix[,32]-para_out$Formica_fusca$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica pratensis
```{r}
cdiff<-para_out$Formica_pratensis$BUGSoutput$sims.matrix[,40]-para_out$Formica_pratensis$BUGSoutput$sims.matrix[,36]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Lasius flavus
```{r}
cdiff<-para_out$Lasius_flavus$BUGSoutput$sims.matrix[,30]-para_out$Lasius_flavus$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Leptothorax acervorum
```{r}
cdiff<-para_out$Leptothorax_acervorum$BUGSoutput$sims.matrix[,36]-para_out$Leptothorax_acervorum$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Tetramorium caespitum
```{r}
cdiff<-para_out$Tetramorium_caespitum$BUGSoutput$sims.matrix[,32]-para_out$Tetramorium_caespitum$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```




#Load data, 200,000 iterations

```{r}
load("C:/Users/julie/Documents/Projects/Occupancy/output/para_out_200_nyr.Rdata") 

para_out <- para_out_200

for(i in 1:length(para_out)) names(para_out)[i] <- para_out[[i]]$SPP_NAM
```

#Species with 200,000 iterations
##Formica exsecta
```{r}
cdiff<-para_out$Formica_exsecta$BUGSoutput$sims.matrix[,30]-para_out$Formica_exsecta$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Formica picea
```{r}
cdiff<-para_out$Formica_picea$BUGSoutput$sims.matrix[,36]-para_out$Formica_picea$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

##Myrmica lobicornis
```{r}
cdiff<-para_out$Myrmica_lobicornis$BUGSoutput$sims.matrix[,33]-para_out$Myrmica_lobicornis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

#Load data, 400,000 iterations

```{r}
load("C:/Users/julie/Documents/Projects/Occupancy/output/para_out_400_nyr.Rdata") 

para_out <- para_out_400

for(i in 1:length(para_out)) names(para_out)[i] <- para_out[[i]]$SPP_NAM
```

#Species with 400,000 iterations
##Lasius niger
```{r}
cdiff<-para_out$Lasius_niger$BUGSoutput$sims.matrix[,30]-para_out$Lasius_niger$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```

#Load data 600,000 iterations
```{r}
load("C:/Users/julie/Documents/Projects/Occupancy/output/para_out_600_nyr.Rdata") 

para_out <- para_out_600

for(i in 1:length(para_out)) names(para_out)[i] <- para_out[[i]]$SPP_NAM
```

#Species with 600,000 iterations
##Lasius meridionalis
```{r}
cdiff<-para_out$Lasius_meridionalis$BUGSoutput$sims.matrix[,30]-para_out$Lasius_meridionalis$BUGSoutput$sims.matrix[,29]
Firsthi<-mean(cdiff < 0) #Highest in first tp
Lasthi<-mean(cdiff > 0) #Highest in last tp
ci_eti <- ci(cdiff, method = "ETi")
mean(cdiff)
ci_eti
Firsthi
Lasthi
```